---
title: "Preview: Sourced Dataframes"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
source("data_input.R")
```

## Introduction

This document is used to test and preview the feed of data from the sourced `data_input.R` file.

At present, the dataset comes from the City of Edinburgh Council's open data sets, and shares attributes about each public CCTV camera in the city.

These attributes include location and ID number.

## Previewing Dataframes

##### df

This is the main dataset, with an added column that takes the initial prefix of the postcode.

```{r dataframe1}
paged_table(
    df
)
```

##### postcode_count

This is a count of cameras by postcode prefix.

```{r dataframe2}
paged_table(
    postcode_count
)
```

##### locality_count

This is a count of cameras by locality.

```{r dataframe3}
paged_table(
    locality_count
)
```

## Plotting Counts

```{r postcode_counts}
ggplot(
  postcode_count,
  aes(
    PostcodePrefix,
    PostcodeCount,
    fill = PostcodeCount
  ) +
    geom_col() +
    labs(x = "Postcode Prefix", y = "CCTV Count") +
    scale_fill_gradient2(high = "green", low = "grey")
)
```

```{r locality_counts}
ggplot(
  locality_count,
  aes(
    Locality,
    LocalityCount,
    fill = LocalityCount
  ) +
    geom_col() +
    labs(x = "Locality", y = "CCTV Count") +
    scale_fill_gradient2(high = "green", low = "grey")
)
```
